BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-06-29 prediction_market_wsc.Rnw
Two minor changes in wording.

Market participation causes traders to converge toward believing the ``true'' climate model under a variety of model parameterizations in a relatively short time: In markets with low segmentation, the number of traders believing the true model rises from 50\% to 75\% in roughly 12 years, and even in highly segmented markets, 75\% convergence is achieved in 18--24 years. Ideally, we would like to compare belief convergence with and without a prediction market but because the only source of climate belief in our current model is market interactions we cannot make this comparison. However, we do use actual temperatures for our model under historical 20th century conditions and observe convergence to the \ce{CO2} model, while in the real world there is no convergence of beliefs.

@@

We thank Yevgeniy Vorobeychik for feedback on this project and Manuel Naumovich Velasco for sharing the data from his Total Solar Irradiance prediction.
U.S. National Science Foundation grants EAR-1416964, EAR-1204685, and 1526860 partially supported this research.
% The funder had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
All views expressed are the authors' and not the funder's.
%We also thank the authors of \href{http://www.r-project.org}{\textsf{R}} \shortcite{r_core}
%and
%\href{http://mc-stan.org}{Stan} \shortcite{Stan2016}.
%This manuscript was prepared using
%RStudio \shortcite{rstudio} and
%knitr \shortcite{xie_knitr_2014}.

>>>>

Market participation causes traders to converge toward believing the ``true'' climate model under a variety of model parameterizations in a relatively short time: In markets with low segmentation, the number of traders believing the true model rises from 50\% to 75\% in roughly 12 years, and even in highly segmented markets, 75\% convergence is achieved in 18--24 years. Ideally, we would like to compare belief convergence with and without a prediction market but because the only source of climate belief in our current model is market interactions we cannot make this comparison. However, we do use actual temperatures for our model under historical 20th century conditions and observe convergence to the \ce{CO2} model, whereas in the real world there is no convergence of beliefs.

@@

We thank Yevgeniy Vorobeychik for feedback on this project and Manuel Naumovich Velasco for sharing the data from his Total Solar Irradiance prediction.
U.S. National Science Foundation grants EAR-1416964, EAR-1204685, and IIS-1526860 partially supported this research.
% The funder had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
All views expressed are the authors' and not the funder's.
%We also thank the authors of \href{http://www.r-project.org}{\textsf{R}} \shortcite{r_core}
%and
%\href{http://mc-stan.org}{Stan} \shortcite{Stan2016}.
%This manuscript was prepared using
%RStudio \shortcite{rstudio} and
%knitr \shortcite{xie_knitr_2014}.
